%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Hieu Do - Resume
% 7/26/2016
%
% Reference:
% Debarghya Das (http://debarghyadas.com)
% !TeX program = xelatex

\documentclass[]{hieudo-build}
\usepackage{datetime2}

\begin{document}
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	%     TITLE NAME
	%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\namesection{Syler Clayton}
	{\urlstyle{same}
		\faEnvelope\href{mailto:syler.clayton@gmail.com}{ Syler.Clayton@gmail.com}\\
		\faPhone \href{tel:+19717129616}{971.712.9616}
		\faGlobe{Bellingham,WA}\\
		\faGlobe\href{http://sylerclayton.com/about}{ SylerClayton.com/about}\\
		\faLinkedin\href{https://www.linkedin.com/in/sylerclayton}{ /SylerClayton}
		\faTwitter\href{https://twitter.com/sylerclayton}{@SylerClayton}
	}
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	%     COLUMN ONE
	%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\begin{minipage}[t]{0.34\textwidth} 
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     EDUCATION
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		\section{Education (M.S.)} 
		
		\subsection{University of Alaska Fairbanks}
		\descript{2008-2014, 3.85 GPA}
		B.S./M.S., Computer Science \\
		Minor, Mathematics
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     SKILLS
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		\section{Skills}
		% \subsection{Programming}
		\begin{tightemize}
		\item Offensive Security
		\item Reverse Engineering
		\item Exploit Development
		\item Red Teaming
		\item Penetration Testing
		\end{tightemize}
		\location{Languages:}
		C, C++, Python, Bash, C\#, Java, PowerShell, JavaScript, Ruby \\ 
		\location{ISAs:}
		x86, PowerPC, ARM, MIPS\\
		\location{Tools:}
		Fortify, BurpSuite, IDA, Ghidra
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     Certifications
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		\section{Certifications}
		OSCP, OSCE, NSTISSI-4011, CNSSI-4013, GIAC GSEC
		% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		% %     Conferences
		% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		\section{Conferences} 
		BSidesPDX, HushCon, RECon, BlackHat, Defcon, DerbyCon, ToorCamp, ShmooCon, Infiltrate
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     COURSEWORK
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		\section{Recent Courses}
		\begin{tightemize}
		\item Applied Physical Attacks
		\item Exploiting RTOS'
		\item Advanced Windows Exploitation
		\item Windows Kernel Rootkits
		\end{tightemize}
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     ADDITIONAL INFORMATION
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%\section{Activities}
		%-UAF Cyber Security  Club \\
		%-CCDC Red Team Lead\\
		%-CFP Review Board (BSidesPDX)
		%\sectionsep
		% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		% %     AWARDS
		% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		\section{Awards} 
		\begin{tightemize}
		\item 1st CCDC Regional
		\item 3rd CCDC National
		\item 2nd MetaCTF
		\item Deans List
		\end{tightemize}
		\sectionsep
		\DTMsetdatestyle{mylastupdate}(Software | Hardware) Exploit? Development\hspace{28em}\DTMsetdatestyle{mylastupdate}\DTMdisplaydate{\the\year}{\the\month}{\the\day}{-1}
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%
		%     COLUMN TWO
		%
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\end{minipage} 
	\hfill
	\begin{minipage}[t]{0.65\textwidth} 
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     EXPERIENCE
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		\section{Experience (11yr)}
		
		\workplace{Oracle - Offensive Security (4yr)}{November 2019 – present}\\
		\position{Senior Offensive Security Engineer}{Remote}
		\vspace{0.9em} % Hacky fix for awkward extra vertical space
		\begin{tightemize}
			\item Full stack security assessments for Oracle's Cloud Infrastructure (OCI) from secure boot to cloud console APIs.
			\item Internal tooling, automation \& metrics.
			\item Contribution to open source software project Cartography.
			\item Change \& Control Review Board Member
		\end{tightemize}
		\sectionsep
		
		\workplace{HP - Offensive Security (4.5yr)}{June 2015 – November 2019}\\
		\position{Lead Application Security Engineer}{Portland, OR}
		\vspace{0.9em} % Hacky fix for awkward extra vertical space
		\begin{tightemize}
			\item Preformed static \& dynamic code analysis, exploit development, penetration testing \& phishing campaigns.
			\item Conducted technical interviews, trained new employees, gave presentations \& mentored an intern.
			\item Malware \& Attack Circle Board Member
		\end{tightemize}
		\sectionsep
		
		\workplace{Resource Data Inc. (1yr)}{May 2014 – June 2015} \\
		\position{Secure Software Developer}{Fairbanks, AK}
		% \vspace{\topsep} % Hacky fix for awkward extra vertical space
		\begin{tightemize}
			\item Reversed proprietary file formats \& implemented parsers.
			\item Identified \& helped remediate critical security vulnerabilities.
		\end{tightemize}
		\sectionsep
		
		\workplace{University of Alaska Fairbanks (2yr)}{August 2012 – May 2014} \\
		\position{Computer Lab Manager/Security Researcher}{Fairbanks, AK}
		% \vspace{\topsep} % Hacky fix for awkward extra vertical space
		\begin{tightemize}
			\item Embedded security research for various devices (DoD grant) \& worked with the University, FBI \& NSA on disclosure.
			\item Managed a lab of 30 machines \& 6 student employees.
			\item Developed a new website for the C.S. department (\href{https://www.cs.uaf.edu/}{cs.uaf.edu}).
			\item Board member for Cyber Security Club. CCDC Red Team Lead.
		\end{tightemize}
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%     PROJECTS
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		\section{Projects}
		\vspace{\topsep} % Hacky fix for awkward extra vertical space
		\begin{tightemize}
			\item {\href{https://github.com/Relys/rewheel}{\underline{OneWheel Reverse Engineering \& Exploit Development}}}
			\item {\href{https://github.com/lyft/cartography}{\underline{Cartography (OCI IAM support)}}}
			\item {\href{https://github.com/wiiudev/libwiiu}{\underline{Nintendo Wii U Exploit Development (libwiiu)}}}
			\item {\href{https://gbatemp.net/threads/release-3ds_ctr_decryptor-void.370684/}{\underline{Nintendo 3DS Decryption Utility (3DS\textunderscore Multi\textunderscore Decryptor)}}}
			\item
			{\underline{Escape From Tarkov Radar using DMA (Private)}}
			\item
			{\underline{AI Prompt Injection (GPT4) \& running local LLMs}}
			\item {\href{https://scholarworks.alaska.edu/handle/11122/9761}{\underline{Intelligent Platform Management Interface Security Research}}}
			\item {\href{https://www.semanticscholar.org/paper/PlayStation-3-System-Architecture-Clayton/9f1819c0ab2370332e2ffcc3a5d1042301f3279ce}{\underline{Playstation 3 System Architecture}}}
		\end{tightemize}
		\sectionsep
	\end{minipage} 
	
\end{document}  
